Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-13 paper/paper.tex
Add SLU vs OSM map images

@@

% TODO: figure with buildings-slu-cropped
% TODO: mention utility buildings inside compounds, source of marginal errors
% TODO: Turning function example figure for a polygon

@@

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_map_compare}
    \caption{Example segments of the Stockholm metropolitan area with unsystematic errors in precision. The SLU building dataset (blue) in superimposed on the OSM dataset (dark gray). The top picture is centered on a city block which shows a semantic mismatching between the two datasets. The whole block consists of only two buildings in the OSM dataset, but is divided into 15 smaller building lots in the SLU dataset. The bottom picture shows 4 smaller buildings whose the positional accuracy is low, due to the buildings being incorrectly scaled, skewed and rotated.}
    \label{fig:space}
\end{figure}

@@

% TODO: Turning function example figure for a polygon

@@

The difference in area cover can partially be explained by small utility buildings that are often not represented in the OpenStreetMap dataset. Particularily the residential areas in downtown, Stockholm, are characteristic in that each city block consists of a street front and an open, communal compound in the middle, inside of which there are usually a number of small utility buildings such as bicycle garages, toolsheds, refuse rooms and such.

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_map_utility_buildings}
    \caption{A map segment which shows an area with many small utility buildings that are represented in the SLU dataset but not in the OSM dataset.}
    \label{fig:space}
\end{figure}
